---
output:
  word_document: default
  html_document: default
  title: "temp_file_important"
author: "LHL"
date: '2020 4 4 '
---

```{r}
library(tidyverse)
library(FNN)
library(parallel)
library(glmnet)
library(pls)
```

```{r}
#load dataset
dat = read.csv("/Users/l604091407/Downloads/final_project.csv")
```

#2.1
```{r,cache=TRUE}
# use blank dataframe to b joined
dat_blank = data.frame(rep(1:nrow(dat),1))

# h index
h = c(3,10,30)

#use for loop to create and join 9 columns to dat_blank
for(i in 1:3){
  for(j in 1:3){ 
  dat_col = dat[,i+1]
  dat_temp = dat %>% mutate(shift = lag(dat_col,h[j])) %>% mutate(temp = ifelse(is.na(shift),dat[1,i+1],shift) , last = (dat[,i+1] - temp) / temp)
  dat_blank = cbind(dat_blank, dat_temp$last)
  }
}
#drop the first column
dat_blank = dat_blank[,-1]

#rename the column
name_first = rep(NA,9)
for(i in 1:3){
  for(j in 1:3){
    name_first[j +(i-1)*3] = paste0("Asset_",i,"_BRet_",h[j])
  }
}
colnames(dat_blank) = name_first
```
\
```{r,eval= FALSE}
#export csv
dat_blank = dat_blank %>%  round(4)
dat_2.1 = write.csv(dat_blank,"/Users/l604091407/Desktop/stats 415 hw/final_project/bret.csv",row.names=FALSE)
```
\
#2.2
```{r,eval=FALSE}
dat_cor = dat_blank[,c(1,4,7)] 
left = nrow(dat_cor) - 21*24*60
first_index = c(rep(1,21*24*60),(1:left))
second_index = 1:nrow(dat_blank)      


Rho_1_2 = rep(NA, 524160)
Rho_2_3 = rep(NA, 524160)
Rho_1_3 = rep(NA, 524160)

for(i in 1:nrow(dat_cor)){
  temp_dat_1 = dat_cor$Asset_1_BRet_3[first_index[i]:second_index[i]]
  temp_dat_2 = dat_cor$Asset_2_BRet_3[first_index[i]:second_index[i]]
  temp_dat_3 = dat_cor$Asset_3_BRet_3[first_index[i]:second_index[i]] 

  Rho_1_2[i] = cor(temp_dat_1,temp_dat_2)
  Rho_1_3[i] = cor(temp_dat_1,temp_dat_3)
  Rho_2_3[i] = cor(temp_dat_2,temp_dat_3)
}

```

\
```{r,eval=FALSE}
corr_dat = corr_dat %>% round(4)
corr_dat[is.na(corr_dat)] = 0
corr_dat
write_csv(corr_dat,"/Users/l604091407/Desktop/stats 415 hw/final_project/corr.csv")
```


```{r,eval=FALSE}
#fill NA with value of 0
corr_dat[is.na(corr_dat)] = 0
```

#2.3
Remark: As we can see from the summary of linear regression below, all the backward returns of Asset 2 and Asset 3 are significant in predicting the forward return of Asset 1 except the 30-min backward return of asset 3. 
\
\
The in-sample correlation between $\hat r_f(t,10)$ and $r_f(t,10)$ is 0.0678748, and the out-of-sample correlation between $\hat r_f(t,10)$ and $r_f(t,10)$ is 0.04067645.
\
\
#It seems that the correlation structure is stable over the year. However, there is some fluctuations in the beginning of the year
```{r}
#dataset of forward return with asset_1 and h = 10
index_forward = c(11:524160,rep(524160,10))

dat_lead = dat %>% mutate(rf_10 = (Asset_1[index_forward] - Asset_1)/Asset_1)

#combine the rf_10 and the backward returns in 2.1
dat_forward = cbind(rf_10 = dat_lead$rf_10 ,dat_blank)

train_set = dat_forward[1:36000,] 
test_set =  dat_forward[360000:360400,] 
```
\
```{r}
#fit the training dataset with linear regression
lm_mod = lm(rf_10~.,data = train_set)

summary(lm_mod)

#the prediciton with linear regression wrt to training set
lm_predict_train = predict(lm_mod,newdata = train_set)

#the prediciton with linear regression wrt to testing set
lm_predict_test = predict(lm_mod,newdata = test_set)

#in-sample correlation
cor(lm_predict_train,train_set$rf_10)
#out-of-sample correlation
cor(lm_predict_test,test_set$rf_10)

```
\
```{r,eval = FALSE}
lm_cor = rep(NA,524160)

#calculate the three week backward returns
left = length(lm_cor) - 21*24*60
first_index = c(rep(1,21*24*60),(1:left))
second_index = 1:length(lm_cor)

#using the train model to predict the whole year rf(t,10)
lm_year_pred = predict(lm_mod,newdata = dat_forward)

for(i in 1:524160){
  temp_year_pred = lm_year_pred[first_index[i]:second_index[i]]
  temp_rf_10 = dat_forward$rf_10[first_index[i]:second_index[i]]
  lm_cor[i] = cor(temp_year_pred,temp_rf_10)
}
lm_cor[1] = 0
# plot the three week backward correlation between rf(t,10)_head and rf(t,10)
plot(lm_cor,cex = 0.5,ylab = "correlation coefficient")
```
#2.4
```{r}
# run KNN with the rest of the K candidates
k_reg_c = c(5,25,50,125,625)
train_mse_knn_c= rep(NA,length(k_reg_c))
test_mse_knn_c = rep(NA,length(k_reg_c))

#run KNN regression 
for(i in 1:length(k_reg_c)){
  train_temp = knn.reg(train = train_set[,-1],test = train_set[,-1],y = train_set$rf_10,k = k_reg_c[i])
  train_mse_knn_c[i] = mean((train_temp$pred - train_set$rf_10)^2)

  test_temp = knn.reg(train = train_set[,-1],test = test_set[,-1],y = train_set$rf_10,k = k_reg_c[i])
  test_mse_knn_c[i] = mean((test_temp$pred - test_set$rf_10)^2)
}


```
\
```{r}
# run KNN with the rest of the K candidates
k_reg_w = c(1000)
train_mse_knn_w= rep(NA,length(k_reg_w))
test_mse_knn_w = rep(NA,length(k_reg_w))


#run KNN regression 
for(i in 1:length(k_reg_w)){
  train_temp = knn.reg(train = train_set[,-1],test = train_set[,-1],y = train_set$rf_10,k = k_reg_w[i])
  train_mse_knn_w[i] = mean((train_temp$pred - train_set$rf_10)^2)

  test_temp = knn.reg(train = train_set[,-1],test = test_set[,-1],y = train_set$rf_10,k = k_reg_w[i])
  test_mse_knn_w[i] = mean((test_temp$pred - test_set$rf_10)^2)
}
```
\
```{r}
k_reg_all = c(k_reg_c,k_reg_w) %>% print()
train_mse_all = c(train_mse_knn_c,train_mse_knn_w) %>% print()
test_mse_all = c(test_mse_knn_c,test_mse_knn_w) %>% print()
test_mse_all
```


```{r}
plot(x = k_reg_all,y = train_mse_all,type = "b",col = "blue",main = "Training and Testing MSE v.s. different K",xlab = "K",ylab = "MSE",lwd = 2)
lines(x = k_reg_all,y = test_mse_all, type = "b", lwd = 2, col = "red")


legend("right", legend = c("Training MSE", "Validation MSE"),
col = c("blue", "red"), cex = .75, lwd = c(2, 2), pch = c(1, 1), lty = c(1, 1))

#optimal K based on the validation MSE
best_k = k_reg_all[which.min(test_mse_all)]  %>% print()

#in-sample correlation between prediction and response 
#train_knn_best = knn.reg(train = train_set[,-1],test = train_set[,-1],y = train_set$rf_10,k = best_k)
#cor(train_knn_best$pred,train_set$rf_10) %>% print()

#out-of-sample correlation between prediction and response 
#test_knn_best = knn.reg(train = train_set[,-1],test = test_set[,-1],y = train_set$rf_10,k = best_k)
#cor(test_knn_best$pred,test_set$rf_10) %>% print()

#prediction of whole year using the optimal K 
#knn_best_all = knn.reg(train = train_set[,-1],test = dat_forward[,-1],y = train_set$rf_10,k = best_k)
#knn_best_all$pred %>% head(10)

#knn_best_all = knn.reg(train = train_set[,-1],test = dat_forward[,-1],y = train_set$rf_10,k = 1)

```

#2.5 Ridge and Lasso
Hello
```{r}
h_ridge = c(3,10,30,60,120,180,240,360,480,600,720,960,1200,1440)

dat_rl_blank = data.frame(rep(1:nrow(dat),1))

#use for loop to create and join 9 columns to dat_blank
for(i in 1:3){
  for(j in 1:length(h_ridge)){ 
  dat_rl_col = dat[,i+1]
  dat_rl_temp = dat %>% mutate(shift_rl = lag(dat_rl_col,h_ridge[j])) %>% mutate(temp = ifelse(is.na(shift_rl),dat[1,i+1],shift_rl) , last = (dat[,i+1] - temp) / temp)
  dat_rl_blank = cbind(dat_rl_blank, dat_rl_temp$last)
  }
}
#drop the first column
data_rl = dat_rl_blank[,-1]

#rename the column
name_rl = rep(NA,42)
for(i in 1:3){
  for(j in 1:14){
    name_rl[j +(i-1)*14] =   paste0("Asset_",i,"_BRet_",h_ridge[j])
  }
}
colnames(data_rl) = name_rl

data_rl_full = cbind(rf_10 = dat_forward$rf_10,data_rl)
```
\
Hello
```{r}
# use prediction matix 
X_rl = model.matrix(rf_10 ~ .,data = data_rl_full)[, -1] 

# y value 
Y_rl = data_rl_full$rf_10

train_index = 1:(nrow(data_rl_full)*0.7)

#set up the training/testing X and Y
train_set_x = X_rl[train_index,] 
train_set_y = Y_rl[train_index]

test_set_x = X_rl[-train_index,]
test_set_y = Y_rl[-train_index] 


#check if the rows match the original dataset
nrow(train_set_x) + nrow(test_set_x)
length(train_set_y) + length(test_set_y)
```
\
###ridge regression
hello
```{r}
#ridge regression
ridge.mod = glmnet(x = train_set_x,train_set_y,alpha = 0)
ridge.pred.test = predict(ridge.mod, newx = test_set_x)
#test MSE
ridge.test.mse = colMeans((ridge.pred.test - matrix(test_set_y , length(test_set_y),ncol(ridge.pred.test)))^2)

ind.min = which.min(ridge.test.mse) 
ridge.lambda = ridge.mod$lambda[ind.min] 

#prediction for whole year
ridge.pred = predict(ridge.mod, s=ridge.lambda, newx=X_rl)
ridge.pred %>% head(10)

#in-sample correlation
cor(ridge.pred[train_index],train_set_y)

#out-of-sample correlation
cor(ridge.pred[-train_index],test_set_y)

```
\
#lasso regression
```{r}
#lasso regression
lasso.mod = glmnet(x = train_set_x,train_set_y,alpha =1)
lasso.pred.test = predict(lasso.mod, newx = test_set_x)
#test MSE
lasso.test.mse = colMeans((lasso.pred.test - matrix(test_set_y , length(test_set_y),ncol(lasso.pred.test)))^2)

ind.min.lasso = which.min(lasso.test.mse)
lasso.lambda = lasso.mod$lambda[ind.min.lasso] 

#prediction for whole year
lasso.pred = predict(lasso.mod, s=lasso.lambda, newx=X_rl) 
lasso.pred %>% head(10)

#in-sample correlation
cor(lasso.pred[train_index],train_set_y)

#out-of-sample correlation
cor(lasso.pred[-train_index],test_set_y)
```
\
#2.6
```{r}
pcr_mse = rep(NA,42)

   asset_pcr = pcr(rf_10~.,data =data_rl_full[train_index,],scale = TRUE,center = TRUE)

for (i in 1:42){
    pcr_pred = predict(asset_pcr,newdata =data_rl_full[-train_index,],ncomp = i)
    pcr_mse[i] = mean((pcr_pred -data_rl_full[-train_index,]$rf_10)^2)
}
best_ncp = which.min(pcr_mse) 
pcr_mse

 #asset_best = pcr(rf_10~.,data =data_rl_full[train_index,],scale = TRUE,center = TRUE,validation = "CV")
 
 #validationplot(asset_best, val.type = "MSEP", legendpos = "topright")
 
```
\
```{r}
#prediction of the whole year 
pcr_pred = predict(asset_pcr,data_rl_full [,names(data_rl_full)!='rf_10'],ncomp=best_ncp)
pcr_pred %>% head(10)

train_size = nrow(data_rl_full) *0.7
#in-sample correlation
cor(data_rl_full[train_index,]$rf_10, pcr_pred[1:train_size]) %>% print()
#out-of-sample correlation
cor(data_rl_full[-train_index,]$rf_10, pcr_pred[-(1:train_size)]) %>% print()
```

```{r}
asset_best = pcr(rf_10~.,data =data_rl_full[train_index,],scale = TRUE,center = TRUE,ncomp = 6)


coef_pcr = coef(asset_best, ncomp = 6, intercept = TRUE)
save(coef_pcr,file = "hello.Rdata")



```






